---
title: "Homework2"
author: "Linfeng Zhou"
date: "September 23, 2015"
output: pdf_document
---

Notes to students:  

1. Going forward, all homework assignments will be produced as notebooks independent of those presented in class.  You may feel free to use the notebooks presented in class to assist you with the homework.  
2. If you have already run a "CAPM" model for some other stock than AAPL and submitted it with Homework 1, please copy and paste your code and results for this homework assignment.  If you did not submit a CAPM for Homework 1, you will not be penalized.  Your "CAPM" model will be grade for this homework assignment.  If you are struggling because, for example, the New York Stock Exchange has a potentially discontinuous price series, please try using Yahoo, which also trades on the NASDAQ.  The goal is not to turn you into finance professionals, but to quickly get you engaged in statistical learning (using a well-understood model) and hypothesis testing.  
3. The question has been raised as to whether students of my class and Dr. Sobolevsky's class may work together on their Foundations Project.  Subject to the other constraints in the syllabus, we approve this request.

Please answer the questions below, disregarding any homework assignments in existing notebooks.


```{r,echo=FALSE,include=FALSE}
## set env
library(foreign)
library(quantmod)
library(ggplot2)
library(plyr)
setwd("~luke/Dropbox/Applied_Data_Science/Assignment 2")
set.seed(1335)
```
### Question 1
1. We discussed at some length the bivariate linear regression model, $$y_i=\beta_0+\beta_1 x_i+\epsilon_i$$  Using R or Python,  generate two series of 1,000 random integers with values between 0 and 9.  Call one series $y$ and the other $x$.  Using R or Python, fit the bivariate linear regression model.  Examine the t-statistic on the coefficient that captures the relationship between $y$ and $x$ to evaluate whether it is greater than two in absolute value.  Would you reject or fail to reject that there is any relationship between these two series?

#### Answer
```{r}
## generate samples
x <- sample(c(0:9), 1000,replace = TRUE) 
y <- sample(c(0:9), 1000,replace = TRUE) 

## formula a linear model
fit1 <- lm(y ~ x)
summary(fit1)
```

##### Comment:
The t-statistics on the coefiicient $x$ is less than two in absolute value. Therefore, we accept the null hypothesis that there is no relationship between these two series.

### Question 2
2. Download the file train.dta from the course website.  These data are formatted as a Stata dataset.  Read this dataset into R or Python.  (For R, you may find the “foreign” library of use.  For Python, we have already installed the Pandas library.  The goal here is to get you familiar with reading datasets with alternative formatting standards.)  Generate summary statistics for the two variables in the data:  (1) $d$, which is an indicator for whether a particular email is spam; and, (2) $x1$, which is an attribute of the email.  Using least squares, regress $d$ on $x1$.  Is the constant statistically significantly different than zero at a 95% level confidence?  Is the coefficient associated with $x1$ statistically significantly different that zero at a 95% level confidence?  Suppose you determine a threshold as to whether an email is spam if the predicted value of $d$ exceeds 1.  In turn, I give you a new email with an attribute value of 0.65 but do not provide a label for the email as to whether it is, in truth, spam.  Given the attribute value of 0.65, would you classify the incoming email as spam or not spam?  Suppose instead I give you another new email with an attribute value of 1.01, but again do not provide a label for the email.  Would you classify it as spam or not spam?
#### Answer
```{r}
setwd("~luke/Dropbox/Applied_Data_Science/Assignment 2")
## import data 
data <- read.dta("train.dta")
```

The summary statistics for the two vairiables in the data are following:
```{r}
### summary data
summary(data)
### fit model
fit2 <- lm(d ~ x1,data)
summary(fit2)
```
According to the result, $x1$ coefficient is significant, however the  constant is not significant.

```{r}
### predict 
data[1001:1002,2] <- c(0.61,1.01)
pred1 <- predict(fit2,data)
pred1[1001:1002] > 1
```

The first mail is not spam, the second one is spam.

### Qustion 3 
3. Using an API such as Quandl, download a daily price series for a particular publicly-traded stock of your choice for a five-year time period (don’t use Apple), as well as the daily price series on the exchange on which it trades.  Using R or Python, calculate the log returns of each series as the natural log of the ratio of (price today/price yesterday).  Use adjusted closing prices as they reflect so-called stock splits.  Using R or Python, generate a histogram of log returns of the stock of your choice.  Using R or Python, generate a scatterplot that relates the log returns of your stock of choice to the log returns of the exchange on which it is traded.  Finally, using R or Python, fit a linear model to obtain estimates of what finance folks call the "alpha" and the "beta".  Is "alpha" significantly different than zero at a 95% level of confidence?  Does a 95% confidence level for "beta" include one?  (Note that your results will depend on the stock price you use.) 

#### Solution
```{r, include=FALSE}
NIKE_INDEX<-getSymbols("NKE",from="2010-09-20", to='2015-09-20',src="yahoo") 
NASQ_INDEX<-getSymbols("^IXIC",from="2010-09-20", to='2015-09-20',src="yahoo")
NIKE_return=log(NKE$NKE.Adjusted/lag(NKE$NKE.Adjusted))
NASQ_return=log(IXIC$IXIC.Adjusted/lag(IXIC$IXIC.Adjusted))
```


```{r}
alldata <- cbind(NIKE_return[,1], NASQ_return[,1])

### eliminate format
write.csv(alldata,"allclean.csv",row.names=FALSE)
d<-read.csv("allclean.csv",header=TRUE)

### plot histogram
NIKE_f = cbind(d$NKE.Adjusted[-1],0)
NASQ_f = cbind(d$IXIC.Adjusted[-1],1)
alldata <- rbind(NIKE_f,NASQ_f)
alldata <- data.frame(alldata)
colnames(alldata) <- c("return","stock")
alldata$stock<-as.factor(alldata$stock)
alldata$stock<-revalue(alldata$stock,c("0"="NIKE","1"="NASDAQ"))
ggplot(alldata,aes(x=return)) + 
  geom_histogram(binwidth=0.003,fill="white",colour="black")+ 
  facet_grid(stock~., scales="free")+
  ggtitle("Histogram of Stock Return")+
  theme_bw()
ggplot(alldata,aes(x=return,fill=stock)) + 
  geom_histogram(binwidth=0.003,position='identity', alpha=0.4)+
  ggtitle("Histogram of Stock Return")+
  theme_bw()

```

```{r}
### plot scatter plot 
alldata1<-cbind(NASQ_f[,1],NIKE_f[,1])
alldata1<-data.frame(alldata1)
colnames(alldata1)<-c("NIKE","NASDAQ")
ggplot(alldata1,aes(x=NASDAQ,y=NIKE)) + geom_point()+
  theme_bw()+ggtitle("CAPM Data")

```
```{r}
### fit linear model 
fit3 <- lm(NIKE~NASDAQ,alldata1)
summary(fit3)

### alpha beta f test 
residuals1 <- fit3$residuals
residuals2 <- NASQ_f[,1] - NIKE_f[,1] 
var.test(residuals1,residuals2)

```

##### Comment 
We reject the null hypothesis. $\alpha$ is not zero, $\beta$ is not include one.